---
title: "2Submission_Metanalysis"
author: "Esteban Agudo"
date: "2023-05-18"
output: html_document
---


```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(metafor)
library(stringr)
library(cowplot)
library(gridExtra)
library(lemon)
library(lme4)
library(metaviz)
library(lemon)
library("rnaturalearth")
library("rnaturalearthdata")
library("sf")
library("ggspatial")
library(sjPlot)
library(reactable)
library(ggpubr)
library(extrafont)
library(scales)
library(fishualize)
library(xlsx)
library(ggpubr)
library("rnaturalearth")
library("rnaturalearthdata")
library("sf")
library("ggspatial")


#loadfonts(device="win") 
colour.palette <- c("#332288", "red3", "#E69F00", "#117733", "#56B4E9","#E69F00",  "#CC79A7", "#D55E00", "#0072B2", "#F0E442", "#CC6677")
```

```{r}
data<-read.csv(file="data.csv", header=TRUE)
str(data)
```

#Exploratory values
Number of experiments per treatment and ecological interaction
```{r}
#Number experiments
data %>% tally

#Number of studies
data %>% distinct(Title)%>% tally

#Number experiments per treatment
data %>% 
  group_by(Treatment)%>%tally

#Number studies per treatment
data %>% 
  group_by(Treatment)%>%distinct(Title)%>%tally

#Number experiments per taxonomic group
data %>% 
  group_by(Tax_Group_specific)%>%distinct(Title)%>%
tally


data %>% 
  group_by(Tax_Group)%>%tally


#Number studies per treatment and tax group
ts<-data %>% 
  group_by(Treatment, Tax_Group)%>%distinct(Title)%>%tally

te<-data %>% 
  group_by(Treatment, Tax_Group)%>%tally

cbind(ts, te$n)

#Number of studies and experimetns in the tropics and temperate
data %>% 
  group_by(Weather)%>%distinct(Title)%>%tally

data %>% 
  group_by(Weather)%>%tally

#Number of studies and experiments per habitat
data %>% 
  group_by(Habitat)%>%distinct(Title)%>%tally

data %>% 
  group_by(Habitat)%>%tally

#Number of studies and experiments considering taxonomic group and interaction
data %>% 
  group_by(Treatment, Interaction)%>%distinct(Title)%>%tally

data %>% 
  group_by(Treatment, Interaction)%>%tally

#Number of studies and experiments considering stressor, and taxonomic group specific
study<-data %>% 
  group_by(Treatment, Tax_Group_specific)%>%distinct(Title)%>%tally %>% print(n=27)

exp<-data %>% 
  group_by(Treatment, Tax_Group_specific)%>%tally %>% print(n=27)

cbind(study, exp$n) #Studies and experiments considering taxonomic group and stressor


significance <-data %>%
  select(Treatment, Significance) %>%
  group_by(Treatment, Significance) %>%
  tally()

significance

data_effect<-data %>%
  filter(Significance=="Significant")%>%
  select(Treatment, #Tax_Group, Significance, 
         Type_Effect) %>%
  group_by(Treatment, #Tax_Group, Significance, 
           Type_Effect)%>%
tally()

# 54, 79, 21

data_effect

data_tax<-data%>%
  filter(Significance=="Significant")%>%
  select(Treatment, Tax_Group, Type_Effect) %>%
  group_by(Treatment, Tax_Group, Type_Effect)%>%
tally()

data_tax
```

Transform into factors
```{r}
data$Tax_Group<-factor(data$Tax_Group)
data$Tax_Group_specific<-factor(data$Tax_Group_specific)
data$Treatment<-factor(data$Treatment)
data$Interaction<-factor(data$Interaction)
data$Habitat<-factor(data$Habitat)

#Ordering some data
data$Significance<-factor(data$Significance, levels=c("Significant", "Non significant", "Not tested"))


```

# Rol of Temperature and acidification on feeding rates
Lets start by normalizing
```{r, message=FALSE, warning=FALSE}
data<-escalc("ROM", m2i = Control_Mean       #log transformed ratio of mean
 , sd2i = Control_SD
 , n2i =Control_n
 , m1i= Treatment_Mean
, sd1i = Treatment_SD
, n1i = Treatment_n
,  data = data, digits = 8)
```

# Histogram of effects
```{r}
head(data)
hist(data$yi)

data<-data %>%
  mutate(Percentage_Effect=(100*(exp(yi)-1)))
  

Effects_Decrease_FR<-data %>%
  filter(Significance=="Significant")%>%
  dplyr::group_by(Treatment) %>%
  filter(Percentage_Effect<0) %>%
  summarise(Mean_effect=mean(Percentage_Effect, na.rm=TRUE), 
            Minimun_decrease=min(abs(Percentage_Effect), na.rm=TRUE),
            Maximun_decrease=max(abs(Percentage_Effect), na.rm=TRUE))
            

Effects_Increase_FR<-data %>%
  filter(Significance=="Significant")%>%
  dplyr::group_by(Treatment) %>%
  filter(Percentage_Effect>0) %>%
  summarise(Mean_effect=mean(Percentage_Effect, na.rm=TRUE), 
            Minimun_Increase=min(abs(Percentage_Effect), na.rm=TRUE),
            Maximun_Increase=max(abs(Percentage_Effect), na.rm=TRUE))

    
  Effect_general<-data %>%
      filter(Significance=Significant)%>%
      dplyr::group_by(Treatment)%>%
      summarise(mean=mean(Percentage_Effect, na.rm=TRUE),
                max=max(Percentage_Effect, na.rm=TRUE), 
                min=min(Percentage_Effect, na.rm=TRUE)) 


data_histogram<-data %>%
  filter(Significance=="Significant") 


data_histogram_table<-data %>%
  filter(Significance=="Significant")%>% 
  select(Treatment, Percentage_Effect) %>%
  group_by(Treatment) %>%
  summarize(min=min(abs(Percentage_Effect)), mean=abs((Percentage_Effect)), max=max(abs(Percentage_Effect)), sd=sd(abs(Percentage_Effect)))


data_warm_hist<-data_histogram %>%
  filter(Treatment=="Warming")

data_acid_hist<-data_histogram %>%
  filter(Treatment=="Acidification")

data_acid_warm_hist<-data_histogram %>%
  filter(Treatment=="Warming+Acidification")

histogram_multistressor<-ggplot(data, aes(x=sign(Percentage_Effect)*(abs(Percentage_Effect))^(1/3)), color=Significance) +    geom_histogram(data=data, aes(fill=Significance))+
  theme_bw()+xlab("Effect size (cubic root of the % change in feeding rates)")+ylab("Number of experiment")+
    geom_vline(xintercept=0, linetype="dashed")+
  theme(axis.title = element_text(size = 7), axis.text=element_text(size=6),  panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
    geom_vline(xintercept=0, linetype="dashed")+
  scale_y_continuous(breaks=seq(0, 22, 2), limits = c(0, 22), expand=c(0, 0))+
  scale_x_continuous(breaks=seq(-6, 14, 2), limits = c(-6, 14), expand=c(0, 0))+
  theme(legend.position = c(.75, .60),
    legend.direction = "vertical",
    legend.justification = c("left", "bottom"),
    legend.box.just = "left",
    legend.margin = margin(1, 1, 1, 1),
    legend.spacing.y = unit(0.05, "cm"),
      legend.text = element_text(size = 8.5, family = "Arial"),
  legend.title=element_text(size=8.5, family = "Arial"),
   legend.key.size = unit(0.4, "cm"),
      legend.key.height = unit(0.4, "cm"))+
   scale_fill_manual(values=colour.palette)+
  labs(fill=NULL)
  
histogram_multistressor
#hist_percentage<-

#cubic root of percentage effect #can't used sqrt or log because I have negative values 

#cubic root of warming effect
hist_warming<-ggplot(data_warm_hist, aes(x=sign(Percentage_Effect)*(abs(Percentage_Effect))^(1/3))) +  #can't used sqrt or log because I have negative values 
  geom_histogram(color="black", fill="black")+
  theme_bw()+xlab("Effect size")+
  ylab("Experiments")+ 
  theme(axis.title = element_text(size = 7), axis.text=element_text(size=6), panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
    geom_vline(xintercept=0, linetype="dashed")+
    scale_x_continuous(breaks=seq(-10, 19, 2), limits=c(-10, 19))+
    scale_y_continuous(breaks=seq(0, 11.5, 1), limits = c(0, 11.5), expand=c(0, 0))

hist_warming

#cubic root of acidification effect
hist_acid<-ggplot(data_acid_hist, aes(x=sign(Percentage_Effect)*(abs(Percentage_Effect))^(1/3))) +  geom_histogram(color="black", fill="black")+
  theme_bw()+xlab("Effect size")+
  ylab("Experiments")+
   theme(axis.title = element_text(size = 7), axis.text=element_text(size=6),  panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
    geom_vline(xintercept=0, linetype="dashed") +
  scale_x_continuous(breaks=seq(-10, 19, 2), limits=c(-10, 19))+
   # scale_x_continuous(breaks=seq(-10, 20, 2))+
    scale_y_continuous(breaks=seq(0, 11.5, 1), limits = c(0, 11.5), expand=c(0, 0))

hist_acid

#sqrt of percentage effect with warming + acidification  
hist_acid_warm<-ggplot(data_acid_warm_hist, aes(x=sign(Percentage_Effect)*sqrt(abs(Percentage_Effect)))) +  #can't used sqrt or log because I have negative values 
  geom_histogram(color="black", fill="black")+
  theme_bw()+xlab("Effect size")+
  ylab("Experiments")+
   theme(axis.title = element_text(size = 7), axis.text=element_text(size=6), panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
    geom_vline(xintercept=0, linetype="dashed")+
   scale_x_continuous(breaks=seq(-10, 19, 2), limits=c(-10, 19))+
    scale_y_continuous(breaks=seq(0, 11.5, 1), limits = c(0, 11.5), expand=c(0, 0))

hist_acid_warm

#Compared with sqrt data including non significant results of both warming and acidificaiton
ggplot(data, aes(x=sign(Percentage_Effect)*sqrt(abs(Percentage_Effect))))+
  geom_histogram(color="black", fill="black")+
  theme_bw()+xlab("sqrt of % effect")+ylab("Number of experiments")+
    geom_vline(xintercept=0, linetype="dashed")


#hist_RatioEffect<-
# logRR of both warming and acidification 
ggplot(data, aes(x=yi)) + 
  geom_histogram(color="black", fill="black")+
  theme_bw()+xlab("Effect (lnRR)")+ylab("Number of experiments")+
  geom_vline(xintercept=0, linetype="dashed")+
  stat_function(fun = dnorm, args = list(mean = mean(data$Percentage_Effect), sd = sd(data$Percentage_Effect)))

#hist_RatioEffect
```

```{r}
hist_comb <- ggarrange(hist_acid, hist_warming, hist_acid_warm
,                  labels = c("A", "B", "C"),
                    ncol = 2, nrow = 2)

hist_comb


hist_comb_multistressor <- ggarrange(histogram_multistressor, 
                  ggarrange(hist_acid, hist_warming, hist_acid_warm, ncol=3, labels=c("B", "C", "D")),
                  labels = c("A"),
                    nrow = 2)

hist_comb_multistressor

```

Figure 2: Histogram of experiments that found significant effects
```{r}
png("Figures/Fig2_HistogramEffects.png", width=15, height=14, units="cm", res=300)
print(hist_comb)
dev.off()


png("Figures/Fig2_HistogramMultistressor.png", width=15, height=14, units="cm", res=300)
print(histogram_multistressor)
dev.off()


png("Figures/Fig2_HistogramCombineMultistressor.png", width=15, height=14, units="cm", res=300)
print(hist_comb_multistressor)
dev.off()



```


```{r}
write.xlsx(data, file = "data_effects.xlsx",
   sheetName = "data_new", append = TRUE)
```

## Metaregressions 

```{r, message=FALSE, warning=FALSE}
#model considering only treatment
model1<- rma.mv(yi,vi, mods =~Treatment-1, random=~1|Title,  method = "REML", knha=TRUE, data = data)
summary(model1)
  
#model considering treatment and interaction
model2<- rma.mv(yi,vi, mods =~Treatment:Interaction-1, random=~1|Title,  method = "REML", knha=TRUE, data = data)
 summary(model2)
  
#model considering treatment, interaction, taxonomic group
model3<- rma.mv(yi,vi, mods =~Treatment:Interaction:Tax_Group-1, random=~1|Title,  method = "REML", knha=TRUE, data = data)
summary(model3)  

#model considering treatment, Weather
model4<- rma.mv(yi,vi, mods =~Treatment*Weather-1, random=~1|Title,  method = "REML", knha=TRUE, data = data)
summary(model4)


#model considering stressor and taxonomic group. For this I am filtering groups that have fewer than 4 and a single study on kelps with two experiments 
levels(data$Treatment)

#data<-data %>%
# filter(!(Treatment=='Acidification' & Tax_Group_specific=='Amphipods')) %>%
  #filter(!(Treatment=='Warming+Acidification' & Tax_Group_specific=='Amphipods')) %>%
  #filter(!(Treatment=='Warming+Acidification' & Tax_Group_specific=='Sea urchins')) %>%
 # filter(!(Treatment=='Warming+Acidification' & Tax_Group_specific=='Crabs')) %>%
  #filter(Temp_variation<11)
  #filter(!(Habitat=="Kelp forest"))%>%
  #filter(!ExpTreatment=="Prey")
  #filter(ExpTreatment=="Both")
 #filter(yi>-3) %>%
 #filter(yi<1.5)
  
# We did several filter to eliminate the studies which have a larger effect and prove this were not determine the significance of results by their own. 
           
#model 7-> Comparing general taxonomic group
model7<- rma.mv(yi,vi, mods =~Treatment:Tax_Group-1, random=~1|Title,  method = "REML", knha=TRUE, data = data)
summary(model7)

model5<- rma.mv(yi,vi, mods =~Treatment:Tax_Group-1, random=~1|Title,  method = "REML", knha=TRUE, data = data)
summary(model5)  

#model considering stressor and specific taxonomic group
model6<- rma.mv(yi,vi, mods =~Treatment:Tax_Group_specific-1, random=~1|Title,  method = "REML", knha=TRUE, data = data)
summary(model6)  

#Comparing models 
AIC(model1, model2, model3, model4, model5, model6)

#Number of studies and experiments considered for metanalysis with taxonomic group
exp<-data %>%
  group_by(Treatment, Tax_Group_specific)%>%
  tally

study<-data%>% 
  group_by(Treatment, Tax_Group_specific)%>%
  distinct(Title) %>%tally
cbind(study, exp$n)

#Number studies and experiments considering general taxonomic group
exp<-data %>%
  group_by(Treatment, Tax_Group)%>%
  tally

study<-data%>% 
  group_by(Treatment, Tax_Group)%>%
  distinct(Title) %>%tally
cbind(study, exp$n)
```

## Effect of type of stressors on predation rates
```{r}
# Model considering only the stressor type model1
comp<-coef(summary(model1)) #get coeficients from model

comp<-setNames(cbind(rownames(comp), comp, row.names = NULL), 
         c("COL1", "estimate", "se", "zval", "pval", "ci.lb", "ci.ub")) # set colnames

new_variables_comp<- gsub("Treatment","",comp$COL1)%>% str_split(":", simplify = TRUE)%>% as.data.frame() %>% cbind(comp) #Separate factors

new_variables_comp_2<- new_variables_comp %>%
  select(V1, estimate, se, zval, pval, ci.lb, ci.ub) %>%
  group_by(V1) #group by factors 

new_variables_comp_2<-as.data.frame(new_variables_comp_2) #make dataframe
```

Creating workbook with data from model measuring effect of stressors
```{r}
write.xlsx(new_variables_comp_2, file = "Models.xlsx",
    sheetName = "Model_Stressors", append = TRUE)
```

Similarly lets plot
```{r, message=FALSE, warning=FALSE}
P1<-ggplot()+
  theme_classic() +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=0.7))+
    labs(x="", y="Effect size on feeding rates(logRR)")+
  geom_hline(yintercept=0, linetype="dashed", 
                  color = "red", size=0.5)+
       geom_jitter(data=data, aes(x=Treatment, y=yi, color=Treatment, shape=Significance, group=Treatment), alpha = 0.2, position = position_jitterdodge(dodge.width=.5, jitter.width =0.9))+
  scale_shape_manual(values=c(16, 21, 10))+
  geom_point(data=new_variables_comp_2, aes(x=V1, y=estimate, color=V1), shape=17, size=2.5, position=position_dodge(width=.5))+
  geom_errorbar(data=new_variables_comp_2, aes(x=V1, color=V1, ymin=ci.ub, ymax=ci.lb), width=0.02, position=position_dodge(.5))+
  scale_fill_manual(values=colour.palette)+
  scale_color_manual(values=colour.palette)+
  scale_y_continuous(breaks = seq(-4,4, 1),limits = c(-4.5,4.2))+
  theme(legend.position = "none")+
  geom_vline(xintercept=c(1.5,2.5), linetype="dashed", size=0.4, color="gray")+guides(shape="none")

P1
```
Figure 2: Effect of stressor on predation rates
```{r}
png("Figures/Fig2_stressor.png", width=10, height=12, units="cm", res=300)
print(P1)
dev.off()
```

## Effect of stressor on predation rates by specific taxonomic group
```{r, message=FALSE, warning=FALSE}
comp<-coef(summary(model6)) #get coeficients from model

comp<-setNames(cbind(rownames(comp), comp, row.names = NULL), 
         c("COL1", "estimate", "se", "zval", "pval", "ci.lb", "ci.ub")) # set colnames

new_variables_comp<- gsub("Treatment|Tax_Group_specific","",comp$COL1)%>% str_split(":", simplify = TRUE)%>% as.data.frame() %>% cbind(comp) #Separate factors

new_variables_comp_2<- new_variables_comp %>%
  select(V1, V2, estimate, se, zval, pval, ci.lb, ci.ub) %>%
  group_by(V1) #group by factors 

new_variables_comp_2<-as.data.frame(new_variables_comp_2) #make dataframe
```

Creating workbook with data from model considering stressor and taxonomic group specific
```{r}
write.xlsx(new_variables_comp_2, file = "Models.xlsx",
     sheetName = "Model_Stressors_TaxGroupSpec", append = TRUE)
```


```{r, r, message=FALSE, warning=FALSE}
P2<-ggplot()+
  theme_classic() +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=0.7))+
    labs(x="", y="Effect size on feeding rates(logRR)", color = "Consumer")+
  geom_hline(yintercept=0, linetype="dashed", 
                  color = "red", size=0.5)+
       geom_jitter(data=data, aes(x=Tax_Group_specific, y=yi, group=Treatment, color=Treatment, shape=Significance), alpha = 0.2, position = position_jitterdodge(dodge.width=.5, jitter.width =0.5))+
  scale_shape_manual(values=c(16, 21, 10))+
  geom_point(data=new_variables_comp_2, aes(x=V2, y=estimate, color=V1), shape=17, size=2.5, position=position_dodge(width=.5))+
  geom_errorbar(data=new_variables_comp_2, aes(x=V2, color=V1, ymin=ci.ub, ymax=ci.lb), width=0.1, position=position_dodge(.5))+
  scale_fill_manual(values=colour.palette)+
  scale_color_manual(values=colour.palette)+
  scale_y_continuous(breaks = seq(-4,4, 1),limits = c(-4.5,4.2))+
  theme(legend.position = c(.05, .90),
    legend.direction = "vertical",
    legend.box = "horizontal",
   legend.justification = c(.01, 0.5),
   legend.box.just = "left",
   #legend.margin = margin(4, 4, 4, 4),
  legend.margin =margin(r=40,l=5,t=5,b=5),
    legend.spacing.y = unit(0.15, "cm"),
      legend.text = element_text(size = 8.5, family = "Times New Roman"),
  legend.title=element_blank(),
   legend.key.size = unit(0.9, "cm"),
   legend.key.height = unit(0.4, "cm"))+
  geom_vline(xintercept=c(1.5,2.5,3.5, 4.5, 5.5), linetype="dashed", size=0.4, color="gray")+guides(shape="none")

P2
```

Figure 3: Effect of stressor on feeding rates by each specific taxonomic group
```{r}
png("Figures/Fig3_stressor_TaxGroup.png", width=18, height=12, units="cm", res=300)
print(P2)
dev.off()
```

## Effect of type of stressors on predation rates by general taxonomic group
```{r}
# Model considering only the stressor type model1
comp<-coef(summary(model7)) #get coeficients from model

comp<-setNames(cbind(rownames(comp), comp, row.names = NULL), 
         c("COL1", "estimate", "se", "zval", "pval", "ci.lb", "ci.ub")) # set colnames

new_variables_comp<- gsub("Treatment|Tax_Group","",comp$COL1)%>% str_split(":", simplify = TRUE)%>% as.data.frame() %>% cbind(comp) #Separate factors

new_variables_comp_2<- new_variables_comp %>%
  select(V1, V2, estimate, se, zval, pval, ci.lb, ci.ub) %>%
  group_by(V1) #group by factors 

new_variables_comp_2<-as.data.frame(new_variables_comp_2) #make dataframe
```


Creating workbook with data from model
```{r}
#Adding data from model considering only stressor
write.xlsx(new_variables_comp_2, file = "Models.xlsx",
   sheetName = "Model_Stressors_TaxGroup", append = TRUE)
```

Similarly lets plot
```{r, message=FALSE, warning=FALSE}
P3<-ggplot()+
  theme_classic() +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=0.7))+
    labs(x="", y="Effect size on feeding rates(logRR)")+
  geom_hline(yintercept=0, linetype="dashed", 
                  color = "red", size=0.5)+
       geom_jitter(data=data, aes(x=Tax_Group, y=yi, color=Treatment, shape=Significance, group=Treatment), alpha = 0.2, position = position_jitterdodge(dodge.width=.5, jitter.width =0.4))+
  scale_shape_manual(values=c(16, 21, 10))+
  geom_point(data=new_variables_comp_2, aes(x=V2, y=estimate, color=V1), shape=17, size=2.5, position=position_dodge(width=.5))+
  geom_errorbar(data=new_variables_comp_2, aes(x=V2, color=V1, ymin=ci.ub, ymax=ci.lb), width=0.1, position=position_dodge(.5))+
  scale_fill_manual(values=colour.palette)+
  scale_color_manual(values=colour.palette)+
  scale_y_continuous(breaks = seq(-4,4, 1),limits = c(-4.5,4.2))+
  theme(legend.position = "none")+
  geom_vline(xintercept=c(1.5,2.5, 3.5), linetype="dashed", size=0.4, color="gray")+guides(shape="none")+ 
  theme(legend.position = c(.05, .90),
    legend.direction = "vertical",
    legend.box = "horizontal",
   legend.justification = c(.01, 0.5),
   legend.box.just = "left",
   #legend.margin = margin(4, 4, 4, 4),
  legend.margin =margin(r=40,l=5,t=5,b=5),
    legend.spacing.y = unit(0.15, "cm"),
      legend.text = element_text(size = 8.5, family = "Times New Roman"),
  legend.title=element_blank(),
   legend.key.size = unit(0.9, "cm"),
   legend.key.height = unit(0.4, "cm"))

P3
```

Figure T2: Effect of stressor on predation rates by general taxonomic group
```{r}
png("Figures/Fig3_stressor_GenTaxGroup.png", width=15, height=12, units="cm", res=300)
print(P3)
dev.off()
```

## Effect of experimental factors on temperature experiments  
```{r}
data_TempSig<-data %>%
  filter(Treatment=="Warming") %>% # %>% 
 filter(!Cons_Aclimatation=="NR")%>% #removing experiments don't report aclimatation
 filter(!Exp_duration=="NR") #filtering experiments don't report days duration 



# Lets model which element determine effect of warming on feeding rates
model_t2<- rma.mv(yi,vi, mods =~Temp_variation+Exp_duration_days
+ExpTreatment+Cons_Aclimatation_days+Starvation, random=~1|Title,  method = "REML", knha=TRUE, data = data_TempSig)

summary(model_t2)

model_t1<- rma.mv(yi,vi, mods =~Temp_variation, random=~1|Title,  method = "REML", knha=TRUE, data = data_TempSig)

summary(model_t1)

#now lets plot a correlation temperature and effect
ggplot(data=data_TempSig, aes(x=Temp_variation, y=yi))+
  geom_point(shape=21)+
  geom_smooth(method=lm, formula=y~x)+
  theme_bw()+
  ylab("Effect size (logRR)")+xlab("Temperature increase (C)")+
  #scale_shape_manual(values=c(16, 21, 8))+
scale_y_continuous(breaks = seq(-1,2, 1),limits = c(-1.5, 2.5))+
scale_x_continuous(breaks = seq(1,15,2),limits = c(0, 15.5))+
    stat_regline_equation(label.x=2, label.y=2) +
        stat_cor(aes(label=..rr.label..), label.x=2, label.y=2)
```
The increase in temperature seems to have a direct effect on the normalize effect size. It is the only experimental factor that had an effect 


Creating excel file with model's results
```{r}
comp<-coef(summary(model_t2)) #get coeficients from model

comp<-setNames(cbind(rownames(comp), comp, row.names = NULL), 
         c("Variable", "estimate", "se", "zval", "pval", "ci.lb", "ci.ub")) # set colnames

new_variables_comp_2<-as.data.frame(comp) #make dataframe
```

Creating workbook with data from model explaining experimental variables affecing warming experiments
```{r}
write.xlsx(new_variables_comp_2, file = "Models.xlsx",
    sheetName = "Model_ExpVar_Warming", append = TRUE)
```

## Effect of methodological factors the effect acidification on feeding rates  
```{r}

data_a<-data %>%
  filter(Treatment=="Acidification")

model_a_only<- rma.mv(yi,vi, mods =~pH_var, random=~1|Title,  method = "REML", knha=TRUE, data = data_a)
summary(model_a_only)

data_AcidSig<-data %>%
  filter(Treatment=="Acidification")%>%
  #filter(Significance=="Significant")%>%
  filter(Acidif_Measure=="pH")%>% #lets use pH as most studies use pH compare to pCO2
  filter(!Cons_Aclimatation=="NR")%>%
  filter(!Exp_duration=="NR") #filtering experiments don't report days duration 


#Lets model effect of experimetnal variables 
model_a1<- rma.mv(yi,vi, mods =~pH_var+Exp_duration_days
+ExpTreatment+Exp_duration_days +ExpTreatment+Cons_Aclimatation_days +Starvation, random=~1|Title,  method = "REML", knha=TRUE, data = data_AcidSig)

summary(model_a1)

#Trying to plot ph variation vs effect
ggplot(data=data_AcidSig, aes(x=pH_var, y=yi))+geom_point()+geom_smooth(method=lm, formula = y~x)+theme_bw()+
 ylab("Effect size (logRR)")+
xlab("Temperature increase (C)")+
scale_y_continuous(breaks = seq(-3, 2, 1),limits = c(-3.8, 1.5))+
scale_x_continuous(breaks = seq(0 ,1, 0.25),limits = c(0.1, 0.9))
```

Creating excel file with model's results
```{r}
comp<-coef(summary(model_a1)) #get coeficients from model

comp<-setNames(cbind(rownames(comp), comp, row.names = NULL), 
         c("Variable", "estimate", "se", "zval", "pval", "ci.lb", "ci.ub")) # set colnames

new_variables_comp_2<-as.data.frame(comp) #make dataframe
```

Creating workbook with data from model explaining experimental variables affecing acidification experiments
```{r}
write.xlsx(new_variables_comp_2, file = "Models.xlsx",
    sheetName = "Model_ExpVar_Acidification", append = TRUE)
```

## Effect of methodological factors the effect acidification+ warming on feeding rates  
```{r}
data_Temp_Acidif<-data %>%
  filter(Treatment=="Warming+Acidification")

model_acid_warming<- rma.mv(yi,vi, mods =~pH_var+Temp_variation +Exp_duration_days+ExpTreatment+Exp_duration_days +ExpTreatment+Cons_Aclimatation_days+Starvation, random=~1|Title,  method = "REML", knha=TRUE, data = data_Temp_Acidif)

summary(model_acid_warming)
```

Creating excel file with model's results
```{r}
comp<-coef(summary(model_acid_warming)) #get coeficients from model

comp<-setNames(cbind(rownames(comp), comp, row.names = NULL), 
         c("Variable", "estimate", "se", "zval", "pval", "ci.lb", "ci.ub")) # set colnames

new_variables_comp_2<-as.data.frame(comp) #make dataframe
```

Writing the data into excel spreedsheet
```{r}
write.xlsx(new_variables_comp_2, file = "Models.xlsx",
    sheetName = "Model_acidf_warm", append = TRUE)
```


## Map with location of studies 

```{r}
world <- ne_countries(scale = "medium", returnclass = "sf")
```

```{r}

studies<-data %>%
  select(Title, Treatment, Longitude, Latitude)%>%
  group_by(Treatment, Longitude, Latitude)%>%
  distinct(Title)

str(studies)

MapStudies<-
  ggplot(data = world)+ 
  geom_sf(color=NA)+
  #let's limit the map area
  coord_sf(xlim = c(-160, 160), ylim = c(-50, 65), expand = FALSE)+
theme_bw()+ 
  theme(axis.title.x=element_blank(),axis.title.y=element_blank(), panel.grid.major = element_line(colour = "white"))+
   geom_point(data=studies, aes(x=Longitude, y=Latitude, colour=Treatment), alpha = 0.5, size=1.6, position = position_jitter(w=1, h=1))+
  scale_colour_manual(values=colour.palette)+
  theme(legend.position = c(.01, .10),
    legend.direction = "vertical",
    legend.justification = c("left", "bottom"),
    legend.box.just = "left",
    legend.margin = margin(1, 1, 1, 1),
    legend.spacing.y = unit(0.05, "cm"),
      legend.text = element_text(size = 9.5, family = "Arial"),
  legend.title=element_text(size=9.2, family = "Arial"),
   legend.key.size = unit(0.4, "cm"),
      legend.key.height = unit(0.4, "cm"))+
  guides(fill = guide_legend(override.aes = list(shape = 21)))

MapStudies
```

Figure 1: Map with location of studies 
```{r}
png("Figures/Fig1_Map.png", width=18, height=12, units="cm", res=300)
print(MapStudies)
dev.off()
```


